CorReg: model based pretreatment for regression with correlated variables. Application in steel industry

### 2014-04-01 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@471 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Clément THERY}
\title{CorReg pretreatment : Regression for correlated variables and application in steel industry}

@@

When one wants to explain a phenomenon based on some covariates, the first statistical method tried frequently is the linear regression. It provides a predictive model with a good interpretability and is simple to learn for non-statistician. Therefore, linear regression is used in nearly all the fields where statistics are made, from industry (ballistic models to calibrate the process) to sociology (predicting some numerical properties of a population).
Linear regression is a very classic situation that faces an also classical problem : the variance of the estimators.
When estimating the parameters of the regression we have to compute the inverse of a matrix\cite{saporta2006probabilites} which will be ill-conditioned or even singular if some covariates depend linearly from each other. For a model defined by 
	\begin{equation}
		Y_{|X}=X\beta + \varepsilon
	\end{equation}
	where $X$ is the $n\times p$ matrix of the explicative variables, $Y$ the response vector and $\varepsilon \sim \mathcal{N}(0,\sigma_Y^2)$ 
	we have the following Ordinary Least Squares (OLS) estimators :
	\begin{equation}
		\hat{\beta}=\left(X'X \right) ^{-1}X'Y
	\end{equation}
	With variance 
	\begin{equation}
		\operatorname{Var}(\hat{\beta})=\sigma_Y^2(X'X)^{-1}
	\end{equation}
	And when correlations between covariates are strong, the matrix to invert is ill-conditioned and the variance explodes.
This variance increases based on two aspects :
\begin{itemize}
	\item The dimension $p$ (number of covariates) of the model  : the more covariates you have the greater variance you get.
	\item The correlations within the covariates : strongly correlated covariates give bad-conditioning and increase variance of the estimators .
\end{itemize}

	With the rise of informatic, datasets contains more and more covariates and thus more and more useless covariates. So dimension reduction becomes a necessity. Moreover, when you use more covariates, you increase the chance to have correlated ones. For example, this work takes place in an industrial (steel industry) context with a big set of covariates (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). In such a context, variance of the estimators can lead to arbitrary results or even no results at all. Prediction and interpretation are both strongly needed, with a preference for interpretation in industrial context (better to improve the process when possible than to only predict defects).
		~\\	~\\

%bibliographie	
	Because OLS is the minimum-variance unbiased estimator, penalized methods try to reduce the variance introducing some bias to improve the bias-variance trade-off and get better prediction.
Moreover, real datasets implies many irrelevant variables (datasets based on the whole process without any a priori) so we have to use variable selection methods.

@@

	Ridge regression\cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \hat{\beta}=\operatorname{argmin} \left\lbrace \parallel Y-X\beta\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\beta\parallel_2^2\leq k
	\end{equation}
	But Ridge regression is not efficient to select covariates (it's an assumed choice) because coefficients tends to 0 but don't reach 0.
	So it gives difficult interpretations for large values of $p$ and is not adapted for our industrial context. We need to reduce the dimension of the model. Our goal is not just to predict but also to understand the response variable.

	The Least Absolute Shrinkage and Selection Operator (LASSO)\cite{tibshirani1996regression} consists in a shrinkage of the regression coefficients based on a $\lambda$ parametric $L_1$ penalty.
		\begin{equation}
		 \hat{\beta}=\operatorname{argmin} \left\lbrace \parallel Y-X\beta\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\beta\parallel_1\leq \lambda
		\end{equation}	
	 The Least Angle Regression\cite{efron2004least} (LAR) Algorithm offers a very efficient way to obtain the whole LASSO path and is very attractive. It requires only the same order of magnitude of computational effort as OLS applied to the full set of covariates. And it  really selects covariates with coeffients set exactly to 0.
	 But LASSO also faces consistency problems \cite{Zhao2006MSC} when confronted  with correlated covariates. Another limitation of the LASSO is that it preserves at most $n$ predictors (troublesome when in high dimension). Some recent variants of the LASSO does exist for the choice of the penalization coefficient like the adaptative LASSO \cite{zou2006adaptive} or the random LASSO \cite{wang2011random}.
	 \\

	Elastic net\cite{zou2005regularization}	is a method developped to be a compromise between Ridge regression and the LASSO. 
%	Given data set $(Y,X)$ and two parameters $(\lambda_1,\lamda_2)$, define artificial data set $(Y^*,X^*)$ by :
%	\begin{equation}
%		X^*_{(n+p)\times p}=(1+\lambda_2)^{-1/2}\left( X  \sqrt{\lambda_2}I \right), \ \ \  Y^*_{(n+p)}=\left( Y 0 \right)
%\end{equation}		
	Elastic net can be written:
	\begin{equation}
		\hat{\beta}=(1+\lambda_2) \operatorname{argmin}\left\lbrace \parallel Y-X\beta \parallel_2^2 \right\rbrace, \textrm{ subject to } (1-\alpha)\parallel\beta\parallel_1+\alpha\parallel\beta\parallel_2^2\leq t \textrm{ for some } t
	\end{equation}
	where $\alpha=\frac{\lambda_2}{(\lambda_1+\lambda_2)}$. 
	It seems to give good predictions. But it is based on the grouping effect and if the dataset contains two identical variables they will obtain the same coefficient whereas LASSO will choose between one of them and will then obtain same predictions with a more parsimonious model. 
	\\

@@

 When some try to reduce the dimension and then just hope to have small correlations in the remaining dimensions,  we propose to focus on the correlations, giving a model with orthogonal covariates and an explicit structure between covariates. In fact we search the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint. This can be viewed as a pretreatment on the dataset allowing to use then other dimension reduction tools without suffering from correlations. We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

@@

But to work, we need an explicit structure between the covariates. SEM are often used in social sciences and economy where a structure is supposed "by hand" but here we want to be able to find a structure without any a priori (possibility to include some known structure remains). Graphical LASSO \cite{friedman2008sparse} offers a method to obtain a structure based on the precision matrix (inverse of the variance-covariance matrix). It consists in a selection in the precision matrix, setting some covariances to zero. But the resulting matrix is symmetric and we need an oriented graph for our SEM. So we developped an MCMC algorithm to find it (R package CorReg on CRAN). However, Graphical LASSO can be used in the initialization step of our MCMC. This structure is based on gaussian mixture models to fit better real datasets and to allow identifiability of the structure in terms of complexity (number of parameters).
 	\\

@@

\section{Model to decorrelate the covariates}

\subsection{Modelisation of the correlations}
Let $Y \in \mathcal{R}^n$ be a response variable we want to explain with a set $X \in \mathcal{R}^{n\times p}$ of $p$ correlated covariates.
We propose to explicitly define a family of $p_2$ internal regressions between covariates whith $I_2$ the set of indices of endogenous variables in $X$ (explained ones) and $I_1=\{I_1^1,\dots,I_1^p \}$ the set of the sets of indices of exogenous covariates (explaining ones) with $\forall j \notin I_2, I_1^j=\emptyset$. Then we have an explicit structure $S=(I_1,I_2,p_1,p_2)$ where $p_1=(p_1^1,\dots,p_1^{p_2})$ is the vector of the number of covariates in each internal regression. Thus we have $p_2=| I_2|$ and $p_1^j=|I_1^j|$ where $|.|$ represents the cardinal of an ensemble.

@@

We can now write the generative model:
\begin{itemize}
	\item Main regression between $Y$ and $X$:
		\begin{equation}
			Y_{|S}=XA+\varepsilon_Y =X_1A_1+X_2A_2+\varepsilon_Y \textrm{ whith } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $A=(A_1,A_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix, 
	\item Family of $p_2$ regressions within correlated covariates in $X$:
		\begin{equation}
			\forall j \in I_2: X^j_{|X_1,S}=X_1B^j_1+\varepsilon_j \textrm{ with } \varepsilon_j \sim(0,\sigma^2_jI_n); \label{SR}
		\end{equation}
		where $B_1^j \in \mathcal{R}^{(p-p_2)}$ are the vectors of the regression coefficients between the covariates (containing some zeros according to $I_1^j$).
\end{itemize}
It remains $p-p_2$ independent exogenous variables : $\forall j \notin I_2 : X^j_{|S} \sim f(\theta_j)$

@@

This generative model is conditional to $S$, the discrete structure model that is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(X,Y)$, the residuals ($\varepsilon_j$) would not stay Gaussian. These residuals are in the following supposed independent but one can suppose dependencies between them and then use appropriate tools to estimate them and the $B_1^j$ like SUR with Feasible Generalized Least Squares (FGLS) by Zellner \cite{SURzellner} or SPRING \cite{chiquetconf} as mentioned in the introduction.
\\
If there are exact regressions ($\sigma^2_j=0$) in (\ref{SR}), the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not really a problem. Moreover, when an exact sub-regression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. \textsc{CorReg} (Our R package) prints a warning to point out exact regressions when found.

\subsection{Estimator and properties}
	We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $X_2$ a regression model on $Y$ {\it depending only on uncorrelated covariates $X_1$}:
	\begin{equation}
		Y=X_1 (A_{1}+ \sum_{j \in I_2}B^{j}_{1}A_{j})+  \sum_{j \in I_2}\varepsilon_{j}A_{j}+\varepsilon_Y 
		 = X_1\alpha_1+ \varepsilon_{\alpha}\label{Trueexpl}
	\end{equation}			
		So we have the unbiased estimator: 
		\begin{equation}
			\hat{\alpha}_{1} = (X'_{1} X^{1})^{-1}X'_{1}Y % \textrm{ and }\hat{\alpha}_{2} = 0
		\end{equation}
		with variance:
		\begin{equation}
			\operatorname{Var}[\hat{\alpha}_{1}|X]= (\sigma^2_Y+\sum_{j \in I_2}\sigma^2_{j}A_{j}^2 )(X'_{1} X^{1})^{-1} % \textrm{ and }\operatorname{Var}[\hat{\alpha}_{2}|X]= 0 
		\end{equation}
		We see that the variance is reduced (no correlations and smaller matrix give better conditioning) for small values of $\sigma_j$ $i.e.$ strong correlations.					
			%There is no theoretical guarantee that our model is better. It's just a compromise between numerical issues caused by correlations for estimation and selection versus increased variability due to structural hypothesis. Therefore we made some simulations to compare both methods (see the end of this paper).
			Moreover, the explicit structure is parsimonious and simply consists in linear regressions and thus is easily understood by non statistician, allowing them to have a better knowledge of the phenomenon inside the dataset. Expert knowledge can even be added to the structure.
			 This new model is reduced even without variable selection and is just a linear regression so every method for variable selection in linear regression can be used. Hence we hope to obtain a parsimonious model with { \it two kinds of zeros}: those from decorrelating step and those from selection step, with different meanings.
			 \\
			 The \textsc{CorReg} package proposes to make selection with both LASSO (with LAR), elasticnet, adaptative lasso, and others more classical methods. A last Ordinary Least Square step is added to improve estimation because penalisation is made to select variables but also shrinks remaining coefficients. This last step allows to keep the benefits of shrinkage (variable selection) without any impact on remaining coefficients (see \cite{SAM10088}).

@@

		Grouping effect is the fact that correlated covariates get similar coefficient and are selected together. It's the case with elasticnet \cite{zou2005regularization} for example.	
			If $X_2=X_1+e$ and we have the grouping effect, we will obtain a model like $\hat{Y}=\hat{a}X_1+\hat{a}X_2$. 
			Then, if you try to modify the response value, you will modify one of the covariates and both will change so you won't get expected results.

		At the opposite, methods like the LASSO with LAR will only keep one covariate for each group of correlated covariates  so we get $\hat{Y}=2aX_1$ and think that $X_2 \perp Y$ but $Y$ depends on $X_2$ so it is worse than grouping effect for interpretation.

			Nothing constrains us to give only one equation. It is clearly better to give the user another equation (or system for more complex models) describing the correlations. 
			So you get the following model : $Y=aX_1+aX_2$ and $X_1=X_2+e$. Then you have more information and are able to decide better actions. 
			With such a model, grouping effect is no more useful because when saying $Y=2aX_1$ and $X_2=X_1+e$ with the information that $X_2$ has been removed locally because of its correlation with $X_1$, you don't get misleading interpretations anymore. In fact, we have two kinds of zeros (those from selection and those from correlations) and we know for each zero which kind is it.
			So it is possible to combine the advantages of grouping effect and selection just giving several equations. 
			Each equation here is very simple (only linear regressions) so you don't really increase complexity of the model. 
			Moreover, the uncrossing constraint ($I_1\cap I_2=\emptyset$) guarantee to keep a simple structure easily interpretable (no cycles and no chain-effect).

	\section{Estimating structure of sub-regressions with a Markov chain}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[table]{xcolor}
 \graphicspath{{figures/}}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Clément THERY, Christophe BIERNACKI, Gaétan LORIDANT}
\title{CorReg: model based pretreatment for regression with correlated variables. Application in steel industry}

@@

When one wants to explain a phenomenon based on some covariates, the first statistical method tried frequently is the linear regression. It provides a predictive model with a good interpretability even  for non-statistician and is simple to learn. Therefore, linear regression is used in nearly all the fields where statistics are made, from industry (ballistic models to calibrate the process) to sociology (predicting some numerical properties of a population).
Linear regression is a very classic situation but sometimes it has to face an also classical problem: the variance of the estimators, even whithout bias from modelisation. 
We note the linear regression model:
\begin{equation}
		Y_{|X}=X\beta + \varepsilon
	\end{equation}
	where $X$ is the $n\times p$ matrix of the explicative variables, $Y$ the  $n\times 1$ response vector and $\varepsilon \sim \mathcal{N}(0,\sigma_Y^2I_n)$ the noise of the regression, with $I_n$ the $n$-sized identity matrix and $\sigma_Y \in \mathcal{R}$. The $p\times 1$ vector $\beta$ is the vector of the coefficients of the regression, estimated with Ordinary Least Squares (OLS) by \cite{saporta2006probabilites} 
	\begin{equation}
		\hat{\beta}=(X'X)^{-1}X'Y.
\end{equation}

When estimating the parameters of the regression we have to compute the inverse of a matrix which will be ill-conditioned or even singular if some covariates depend linearly from each other. 
Variance of $\hat{\beta}$ increases based on two aspects :
\begin{itemize}
	\item The dimension $p$ (number of covariates) of the model  : the more covariates you have the greater variance you get.
	\item The correlations within the covariates : strongly correlated covariates give bad-conditioning and increase variance of the estimators .
\end{itemize}

	With the rise of informatic, datasets contains more and more covariates and thus more and more useless covariates. So dimension reduction becomes a necessity. Moreover, when you use more covariates, you increase the chance to have correlated ones.  It will be illustrated with examples from steel industry in the last section of this paper with a big set of covariates (many parameters of the whole process without any a priori) highly correlated (physical laws, process rules, etc). In such a context, variance of the estimators can lead to arbitrary results or even no results at all. Prediction and interpretation are both strongly needed, depending on the context. For instance, in an industrial context interpretation could be favored to improve the process instead of only predict defects.
		~\\	~\\

%bibliographie	
	Because OLS is the minimum-variance unbiased estimator, penalized methods try to reduce the variance introducing some bias to improve the bias-variance trade-off and get better prediction.
Moreover, real datasets imply many irrelevant variables so we have to use variable selection methods.

@@

	Ridge regression\cite{marquardt1975ridge} proposes a biased estimator that can be written in terms of a parametric $L_2$ penalty:
	\begin{equation}
		 \hat{\beta}=\operatorname{argmin} \left\lbrace \parallel Y-X\beta\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\beta\parallel_2^2\leq k
	\end{equation}
	But Ridge regression do not aim at selecting covariates because coefficients tends to 0 but don't reach 0.
	So it gives difficult interpretations for large values of $p$.

	The Least Absolute Shrinkage and Selection Operator (LASSO)\cite{tibshirani1996regression} consists in a shrinkage of the regression coefficients based on a $\lambda$ parametric $L_1$ penalty.
		\begin{equation}
		 \hat{\beta}=\operatorname{argmin} \left\lbrace \parallel Y-X\beta\parallel_2^2 \right\rbrace \textrm{ subject to } \parallel\beta\parallel_1\leq \lambda
		\end{equation}	
	 The Least Angle Regression\cite{efron2004least} (LAR) Algorithm offers a very efficient way to obtain the whole LASSO path and is very attractive. It requires only the same order of magnitude of computational effort as OLS applied to the full set of covariates. And it  really selects covariates with coefficients set exactly to 0.
	 But LASSO also faces consistency problems \cite{Zhao2006MSC} when confronted  with correlated covariates. Another limitation of the LASSO is that it preserves at most $n$ predictors (troublesome when in high dimension). Some recent variants of the LASSO does exist for the choice of the penalization coefficient like the adaptative LASSO \cite{zou2006adaptive} or the random LASSO \cite{wang2011random}.
	 \\

	Elastic net\cite{zou2005regularization}	is a method developed to be a compromise between Ridge regression and the LASSO. 
%	Given data set $(Y,X)$ and two parameters $(\lambda_1,\lamda_2)$, define artificial data set $(Y^*,X^*)$ by :
%	\begin{equation}
%		X^*_{(n+p)\times p}=(1+\lambda_2)^{-1/2}\left( X  \sqrt{\lambda_2}I \right), \ \ \  Y^*_{(n+p)}=\left( Y 0 \right)
%\end{equation}		
	Elastic net can be written:
	\begin{equation}
		\hat{\beta}=(1+\lambda_2) \operatorname{argmin}\left\lbrace \parallel Y-X\beta \parallel_2^2 \right\rbrace, \textrm{ subject to } (1-\alpha)\parallel\beta\parallel_1+\alpha\parallel\beta\parallel_2^2\leq t \textrm{ for some } t
	\end{equation}
	where $\alpha=\frac{\lambda_2}{(\lambda_1+\lambda_2)}$. 
	%It seems to give good predictions. 
	But it is based on the grouping effect and if the dataset contains two identical variables they will obtain the same coefficient whereas LASSO will choose between one of them and will then obtain same predictions with a more parsimonious model. 
	\\

@@

 Where some try to reduce the dimension and then just hope to have small correlations in the remaining dimensions,  we propose to focus on the correlations, giving a model with orthogonal covariates and an explicit structure between covariates. In fact we search the greatest set of orthogonal covariates to keep the maximum information but with an orthogonality constraint. This can be viewed as a pretreatment on the dataset allowing to use then other dimension reduction tools without suffering from correlations. %We only consider strong correlations (i.e. : problematic ones) thus we keep most of the information contained in the dataset. 
 %We will in a second time be able to use the remaining part of the information (sequential approach).

@@

But to work, we need an explicit structure between the covariates. SEM are often used in social sciences and economy where a structure is supposed "by hand" but here we want to be able to find a structure without any a priori (possibility to include some known structure remains). Graphical LASSO \cite{friedman2008sparse} offers a method to obtain a structure based on the precision matrix (inverse of the variance-covariance matrix). It consists in a selection in the precision matrix, setting some covariances to zero. But the resulting matrix is symmetric and we need an oriented graph for our SEM. So we developped an MCMC algorithm to find it (R package CorReg on CRAN). However, Graphical LASSO can be used in the initialization step of our MCMC. This structure is based on a generative model to be able to compare likelihood-based criterion	 in the MCMC.
 	\\

@@

\section{Model to select decorrelated covariates}
\subsection{The decorrelation problem in regression}
For a model defined by 
	\begin{equation}
		Y_{|X}=X\beta + \varepsilon
	\end{equation}
	where $X$ is the $n\times p$ matrix of the explicative variables, $Y$ the response vector and $\varepsilon \sim \mathcal{N}(0,\sigma_Y^2I_n)$ with $I_n$ the $n$-sized identity matrix,
	we have the following Ordinary Least Squares (OLS) estimators:
	\begin{equation}
		\hat{\beta}=\left(X'X \right) ^{-1}X'Y
	\end{equation}
	With variance 
	\begin{equation}
		\operatorname{Var}(\hat{\beta})=\sigma_Y^2(X'X)^{-1} \label{eqOLS}
	\end{equation}
	 The Mean Squared Error (MSE) on $\hat{\beta}$ is:
	\begin{eqnarray}
		MSE(\hat{\beta}|\beta,X)&=&Bias^2+\operatorname{Tr}(\operatorname{Var}(\hat{\beta})) \\
			&=&0+\sigma_Y^2 \operatorname{Tr}((X'X)^{-1})
	\end{eqnarray}	 
	and when correlations between covariates are strong, the matrix to invert is ill-conditioned, the variance explodes and so does the MSE.
\subsection{Modelisation of the correlations}
Let now $X \in \mathcal{R}^{n\times p}$ be a set of $p$ correlated covariates.
We propose to explicitly define a family of $p_2$ internal regressions between covariates whith $I_2$ the set of indices of endogenous variables in $X$ (explained ones) and $I_1=\{I_1^1,\dots,I_1^p \}$ the set of the sets of indices of exogenous covariates (explaining ones) with $\forall j \notin I_2, I_1^j=\emptyset$. Then we have an explicit structure $S=(I_1,I_2,p_1,p_2)$ where $p_1=(p_1^1,\dots,p_1^{p_2})$ is the vector of the number of covariates in each internal regression. Thus we have $p_2=| I_2|$ and $p_1^j=|I_1^j|$ where $|.|$ represents the cardinal of an ensemble.

@@

We define a family of $p_2$ regressions within correlated covariates in $X$:
	\begin{equation}
		\forall j \in I_2: X^j_{|X_1,S}=X_1B^j_1+\varepsilon_j \textrm{ with } \varepsilon_j \sim(0,\sigma^2_jI_n) \label{SR}
	\end{equation}
		where $B_1^j \in \mathcal{R}^{(p-p_2)}$ are the vectors of the regression coefficients between the covariates (containing some zeros according to $I_1^j$).
It remains $p-p_2$ independent exogenous variables : $\forall j \notin I_2 : X^j_{|S} \sim f(\theta_j)$

@@

This generative model is conditional to $S$, the discrete structure model that is identifiable because we can't permute some regressions in (\ref{SR}) and obtain the same joint distribution $P(X,Y)$, the residuals ($\varepsilon_j$) would not stay Gaussian (see the appendices). These residuals are in the following supposed independent but one can suppose dependencies between them and then use appropriate tools to estimate them and the $B_1^j$ like SUR with Feasible Generalized Least Squares (FGLS) by Zellner \cite{SURzellner} or SPRING \cite{chiquetconf} as mentioned in the introduction.
\\
If there are exact regressions ($\sigma^2_j=0$) in (\ref{SR}), the structure won't be identifiable. But it only means that several structure will have the same likelihood and they will have the same interpretation. So it's not really a problem. Moreover, when an exact sub-regression is found, we can delete one of the implied variables without any loss of information and the structure will define a list of variable from which to delete. %\textsc{CorReg} (Our R package) prints a warning to point out exact regressions when found.

\subsection{Marginal regression model with decorrelated covariates}
Let $Y \in \mathcal{R}^n$ be a response variable we want to explain with $X$.
We note that (\ref{MainR}) and (\ref{SR}) also give by simple integration on $X_2$ a regression model on $Y$ {\it depending only on uncorrelated covariates $X_1$}:
		\begin{equation}
			Y_{|S,X}=X\beta+\varepsilon_Y =X_1\beta_1+X_2\beta_2+\varepsilon_Y \textrm{ whith } \varepsilon_Y \sim \mathcal{N}(0,\sigma^2_YI_n);	\label{MainR}
		\end{equation}
		where $\beta=(\beta_1,\beta_2) \in  \mathcal{R}^p$ is the vector of the regression coefficients and $I_n$ the identity matrix. 
Knowing (\ref{SR}) we then obtain a marginal regression model:
\begin{eqnarray}
	Y_{|X_1}&=&X_1 (\beta_{1}+ \sum_{j \in I_2}B^{j}_{1}\beta_{j})+  \sum_{j \in I_2}\varepsilon_{j}\beta_{j}+\varepsilon_Y \label{Trueexpl} \\
		&=&X_1 \alpha_1 + X_2\alpha_2 + \varepsilon_{\alpha} \textrm{ where} \alpha_2  = 0.
\end{eqnarray}
We note that it simply is a linear regression on some of the original covariates so we only made a pretreatment on the dataset by setting some coefficients to $0$ because of correlations. These $0$ won't be interpreted as independence with the response variable but as redundant information due to correlations between the covariates. It isa variable pre-selection independent of the response $Y$. As a pretreatment, it allows usage of any method in a seconde time to estimate $\alpha$.
\subsection{Estimator and properties}
	The marginal regression model simply is
	\begin{equation}
		Y_{|X_1}= X_1\alpha_1+ \varepsilon_{\alpha}
	\end{equation}			
		So we have the unbiased estimator of $\alpha$: 
		\begin{equation}
			\hat{\alpha}_{1} = (X'_{1} X_{1})^{-1}X'_{1}Y  \textrm{ and }\hat{\alpha}_{2} = 0
		\end{equation}
		We see in (\ref{Trueexpl}) that it gives an unbiased estimation of $Y$ and $\alpha$
		but in terms of $\beta$ this estimator is biased:
		\begin{equation}
			\operatorname{E}[\hat{\alpha_1}|X_1]=\beta_1+\sum_{j \in I_2}B^{j}_{1}\beta_{j}\textrm{ and }\operatorname{E}[\hat{\alpha_2}|X_1]=0
		\end{equation}
		with variance:
		\begin{equation}
			\operatorname{Var}[\hat{\alpha}_{1}|X_1]= (\sigma^2_Y+\sum_{j \in I_2}\sigma^2_{j}\beta_{j}^2 )(X'_{1} X_{1})^{-1}  \textrm{ and }\operatorname{Var}[\hat{\alpha}_{2}|X_1]= 0 
		\end{equation}
		We see that the variance is reduced compared to OLS described in equation (\ref{eqOLS})(no correlations and smaller matrix give better conditioning ) for small values of $\sigma_j$ $i.e.$ strong correlations.					
			%There is no theoretical guarantee that our model is better. It's just a compromise between numerical issues caused by correlations for estimation and selection versus increased variability due to structural hypothesis. Therefore we made some simulations to compare both methods (see the end of this paper).
			Moreover, the explicit structure is parsimonious and simply consists in linear regressions and thus is easily understood by non statistician, allowing them to have a better knowledge of the phenomenon inside the dataset. Expert knowledge can even be added to the structure.
			 This new model is reduced even without variable selection and is just a linear regression so every method for variable selection in linear regression can be used then,like LASSO or even stepwise \cite{seber2012linear}. Hence we hope to obtain a parsimonious model with { \it two kinds of zeros}: those from decorrelating step and those from selection step, with different meanings.
			 \\
			  A last Ordinary Least Square step is added to improve estimation because penalisation is made to select variables but also shrinks remaining coefficients. This last step allows to keep the benefits of shrinkage (variable selection) without any impact on remaining coefficients (see \cite{SAM10088}).

	To better illustrate the bias-variance compromise, we look at a simple example with $p=3$ variables. $X_1$ is composed by two independent scaled Gaussian $\mathcal{N}(0,1)$, $X_3=\frac{1}{2}x_1+\frac{1}{2}x_2+\varepsilon_3$ where $\varepsilon_3\sim{\mathcal{N}(0,\sigma_3^2)}$. We also have $\beta=(\frac{1}{3},\frac{1}{3},\frac{1}{3})$ and $\sigma_Y=10$. Then we observe the theoretical Mean Squared Error (MSE) of the estimator of both OLS and \textsc{CorReg} model: $MSE(\hat{\beta}|\beta,X)=Bias^2+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}))$ for several values of $\sigma_3$ (strength of the sub-regression) and $n$. Figures \ref{MQE1} to \ref{MQE3} show the theoretical MSE evolution with the strength of the sub-regression:
	\begin{equation}
		1-\mathcal{R}^2=\frac{\operatorname{Var}(\varepsilon_3)}{\operatorname{Var}(x_3)}=\frac{\sigma_3^2}{\sigma_3^2+\frac{1}{2}}
	\end{equation}

\begin{figure}[h!]
	\begin{minipage}[l]{.32\linewidth}
			\includegraphics[width=170px]{figures/MQEn15sigmaY10.png} 
			\caption{For $n=15$. Dotted: \textsc{Correg}, plain: OLS}\label{MQE1}
	\end{minipage} \hfill
	\begin{minipage}[c]{.32\linewidth}
			\includegraphics[ width=170px]{figures/MQEn100sigmaY10.png} 
			\caption{For $n=100$. Dotted: \textsc{Correg}, plain: OLS}
	\end{minipage} \hfill
   \begin{minipage}[r]{.32\linewidth}
			\includegraphics[width=170px]{figures/MQEn1000sigmaY10.png} 
			\caption{For $n=1000$. Dotted: \textsc{Correg}, plain: OLS.} \label{MQE3}
   \end{minipage} 
\end{figure} 
It is clear in Figures \ref{MQE1} to \ref{MQE3} that the reduced model is more robust than OLS. And even when sub-regression are week (small value of $1-\mathcal{R}^2$) it does not explode. We also see that the error implied by strong correlations shrinks whit the rise of $n$.  $MSE_{OLS}=0+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}))=\operatorname{Tr}(\operatorname{Var}(\hat{\beta}_{1}))+\operatorname{Tr}(\operatorname{Var}(\hat{\beta}_{2}))$. both terms are multiplied by $\sigma_Y^2$ and so is $\operatorname{Tr}(\operatorname{Var}(\hat{\alpha}_{1}))$. Thus, as $\operatorname{Var}(\hat{\alpha}_{1})=0$ when $\sigma_Y^2$ rises it increases the advantage of \textsc{CorReg} versus OLS. It illustrates the importance of dimension reduction when the model has a strong noise (very usual case on real datasets where true model is not even exactly linear).

@@

		Grouping effect is the fact that correlated covariates get similar coefficient and are selected together. It's the case with elasticnet \cite{zou2005regularization} for example.	
			If $X_2=X_1+e$ and we have the grouping effect, we will obtain a model like $\hat{Y}=\hat{\beta}X_1+\hat{\beta}X_2$. 
			Then, if you try to modify the response value, you will modify one of the covariates and both will change so you won't get expected results.

		%At the opposite, methods like the LASSO with LAR will only keep one covariate for each group of correlated covariates  so we get $\hat{Y}=2aX_1$ and think that $X_2 \perp Y$ but $Y$ depends on $X_2$ so it is worse than grouping effect for interpretation.

			Nothing constrains us to give only one equation. %It is clearly better to give the user another equation (or system for more complex models) describing the correlations. 
			If you have the following model : $Y=\beta X_1+\beta X_2$ and $X_1=X_2+e$. Then you have more information and are able to decide better actions. 
			With such a model, grouping effect is no more useful because when saying $Y=2\beta X_1$ and $X_2=X_1+e$ with the information that $X_2$ has been removed locally because of its correlation with $X_1$, you don't get misleading interpretations anymore. In fact, we have two kinds of zeros (those from selection and those from correlations) and we know for each zero which kind is it.
			So it is possible to combine the advantages of grouping effect and selection just giving several equations. 
			Each equation here is very simple (only linear regressions) so you don't really increase complexity of the model. 
			Moreover, the uncrossing constraint ($I_1\cap I_2=\emptyset$) guarantee to keep a simple structure easily interpretable (no cycles and no chain-effect) and straightforward readable.

	\section{Estimating structure of sub-regressions with a Markov chain}	
\subsection{Detailed generative model}
	To be able to compare structures with probabilistic criterions, we need a full generative model. We suppose that variables in $X_1$ follow Gaussian mixtures. 
	\begin{equation}
			\forall j \notin I_2 : X^j_{|S} \sim f(\theta_j)=\mathcal{GM}(\pi_j;\mu_j;\sigma^2_j) \textrm{ with } \pi_j,\mu_j,\sigma^2_j \textrm{ vectors of size } k_j; \label{mixtureX1}
		\end{equation}
		The great flexibility \cite{mclachlan2004finite} of such models makes our model more robust but one can use other laws if needed. Gaussian case is just a special case ($k_j=1$) of Gaussian mixture so it is included in our hypothesis.
